### 2014-02-18 classicthesis/RelatedWork.tex
late night work, WoS
FPGA apprach

Defined search query resulted in 65 documents.

@@

@@

>>>>

The defined search query resulted in 65 documents.

@@

The defined search query resulted in 16 documents. Three of those documents were also present in the set of 65 documents found using Scopus.

@@

\section{FPGA-based LambdaRank}
Yan et al\cite{Yan2009,Yan2010,Yan2011,Yan2012} described the development and incremental improvement of a \ac{SIMD} architecture \ac{FPGA} designed to run the Neural Network based LambdaRank Learning-to-Rank algorithm. This architecture achieved a 29.3X speed-up compared to the software implementation when evaluated on data from a commercial search engine. The exploration of \ac{FPGA} for Learning-to-Rank showed other advantages of the \ac{FPGA} approach next to faster model training. In their latest publication\cite{Yan2012} the FPGA based LambdaRank implementation showed it could achieve up to 19.52X power efficiency and 7.17X price efficiency for query processing compared to Intel Xeon servers currently used at the commercial search engine.
